---
title: "Stats_with_function"
author: "R.Welch"
date: "2025-03-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

libraries
```{r : reading libraries, include= FALSE}
packages <- c("tidyverse", "readxl", "dplyr", "magrittr", "mixtools", "emmeans", "readr","data.table", "lubridate", "ggplot2", "skimr", "ggstatsplot","summarytools", "knitr", "here", "ggthemes", "Amelia", "tidyr", "naniar", "stringr", "janitor")

lapply(packages, library, character.only = TRUE)
```

Want to achieve:
- combine Nov23-Nov24 with Nov24-Feb25 (because Nov24-Feb25 only has 10 data points)
- total daily standarised doses for each medication
- flag HC daily dose <8mg and >20mg per BSA
- add n number to stats
- performs stats on all other numerical fields from minimal dataset (e.g.: height,         weight, BMI, renin, testosterone, glucose, BPs)
- look at dose timings, per centre per drug
- 17 ohp and andro lab values women vs men per centre
- HC dose trends per centre (including individual doses and total daily doses)
- blood pressure - spread of values for both diastolic vs systolic and subsequent        categories

I have processed data in excel for now, so I'll start by reading that in here to use as a starting point for this analysis.


```{r : reading in data}
Nov22_Nov23_minimal_dataset <- read.csv("C:/Users/md1rwe/Documents/Data extractions from I-CAH/Feb 2025/SDM_stats/data/Nov22-Nov23.csv", header=T, na.strings= c("", "NA"))

Nov23_Nov24_minimal_dataset <- read.csv("C:/Users/md1rwe/Documents/Data extractions from I-CAH/Feb 2025/SDM_stats/data/Nov23-Nov24.csv", header=T, na.strings= c("", "NA"))

Nov24_Feb25_minimal_dataset <- read.csv("C:/Users/md1rwe/Documents/Data extractions from I-CAH/Feb 2025/SDM_stats/data/Feb25-Nov24.csv", header=T, na.strings= c("", "NA"))
```


Let's merge Nov23-Nov24 to Nov24-Feb25
```{r : making Nov23-Feb25}
Nov23_Feb25_minimal_dataset <- rbind(Nov23_Nov24_minimal_dataset, Nov24_Feb25_minimal_dataset)

# remove the two now individual frames

remove(Nov23_Nov24_minimal_dataset, Nov24_Feb25_minimal_dataset)
```

Let's format date fields properly
```{r : formatting date fields}
Nov22_Nov23_minimal_dataset$Date.of.Assessment <- as.Date(Nov22_Nov23_minimal_dataset$Date.of.Assessment, format = "%d/%m/%Y")

Nov23_Feb25_minimal_dataset$Date.of.Assessment <- as.Date(Nov23_Feb25_minimal_dataset$Date.of.Assessment, format = "%d/%m/%Y")
```

Use this function to simplify making stats for numerical data in the minimal data set

############################
```{r}

summariseStat <- function(statName, minimalDataset) {

colNames <- names(minimalDataset)
nameIdx <- colNames == statName

if (sum(nameIdx) == 0) {
  print(sum(nameIdx))
  print("no variable with that name")
  return (FALSE)
}

stat <- as.vector(minimalDataset[,nameIdx])

StatSummary <- minimalDataset %>%
  summarise("mean" = mean(stat, na.rm = T),
            "median" = median(stat, na.rm = T),
            "SD" = sd(stat, na.rm = T),
            "min" = min(stat, na.rm = T),
            "max" = max(stat, na.rm = T),
            "n" = length(stat[!is.na(stat)])) %>%
  mutate_if(is.numeric, ~round(., 2))

print(StatSummary)

## change shape of data frame
statSummaryFrame <- data.frame(cbind(names(StatSummary), t(StatSummary)))
statSummaryFrame <- select(statSummaryFrame, -X1)
colnames(statSummaryFrame) <- c(statName)

return (statSummaryFrame)

}
```



#########
```{r}
summariseStatGroup <- function(statName, minimalDataset) {

colNames <- names(minimalDataset)
nameIdx <- colNames == statName

if (sum(nameIdx) == 0) {
  print(sum(nameIdx))
  print("no variable with that name")
  return (FALSE)
}

stat <- as.vector(minimalDataset[,nameIdx])

variableforsummary <- minimalDataset[]

StatSummary <- minimalDataset %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("mean" = mean(stat, na.rm = T),
            "median" = median(stat, na.rm = T),
            "SD" = sd(stat, na.rm = T),
            "min" = min(stat, na.rm = T),
            "max" = max(stat, na.rm = T),
            "n" = length(stat[!is.na(stat)])) %>%
  mutate_if(is.numeric, ~round(., 2))

print(StatSummary)

## change shape of data frame
statSummaryFrame <- data.frame(cbind(names(StatSummary), t(StatSummary)))
statSummaryFrame <- select(statSummaryFrame, -X1)
colnames(statSummaryFrame) <- c(statName)

return (statSummaryFrame)

}
```









##########
TO USE THIS FUNCTION:
nameof_df_youwant <- summariseStat("name of element", df that contains the element)

```{r}
# anthropometry
height_22_23 <- summariseStat("Height..cm.", Nov22_Nov23_minimal_dataset)
weight_22_23 <- summariseStat("Weight..kg.", Nov22_Nov23_minimal_dataset)
BMI_22_23 <- summariseStat("BMI", Nov22_Nov23_minimal_dataset)
BSA_22_23 <- summariseStat("BSA..no.height.available.", Nov22_Nov23_minimal_dataset)
Sys.BP_22_23 <- summariseStat("Systolic.Blood.Pressure", Nov22_Nov23_minimal_dataset)
Dias.BP_22_23 <- summariseStat("Diastolic.Blood.Pressure", Nov22_Nov23_minimal_dataset)
Age_22_23 <- summariseStat("Age", Nov22_Nov23_minimal_dataset)

# labs
# these stats are for all data in the timeframe, both women and men combined.
# to be useful, these need to be split into sex categories (and then into centres)
plasma_renin_22_23 <- summariseStat("Renin.plasma.activity", Nov22_Nov23_minimal_dataset)
testosterone_22_23 <- summariseStat("Total.testosterone.value", Nov22_Nov23_minimal_dataset)
andro_22_23 <- summariseStat("Androstenedione.value", Nov22_Nov23_minimal_dataset)
```

```{r : joining stat frames}
anthropometry_stats_22_23 <- cbind(height_22_23, weight_22_23, Age_22_23, BMI_22_23, BSA_22_23, Sys.BP_22_23, Dias.BP_22_23)
```



############################
