---
title: "Stats"
author: "R.Welch"
date: "2025-03-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

libraries
```{r : reading libraries, include= FALSE}
packages <- c("tidyverse", "readxl", "dplyr", "magrittr", "mixtools", "emmeans", "readr","data.table", "lubridate", "ggplot2", "skimr", "ggstatsplot","summarytools", "knitr", "here", "ggthemes", "Amelia", "tidyr", "naniar", "stringr", "janitor", "ggbreak", "patchwork", "plotrix", "viridis", "hrbrthemes", "showtext")

lapply(packages, library, character.only = TRUE)
```

Want to achieve:
- combine Nov23-Nov24 with Nov24-Feb25 (because Nov24-Feb25 only has 10 data points)
- total daily standarised doses for each medication
- flag HC daily dose <8mg and >20mg per BSA
- add n number to stats
- performs stats on all other numerical fields from minimal dataset (e.g.: height,         weight, BMI, renin, testosterone, glucose, BPs)
- look at dose timings, per centre per drug
- 17 ohp and andro lab values women vs men per centre
- HC dose trends per centre (including individual doses and total daily doses)
- blood pressure - spread of values for both diastolic vs systolic and subsequent        categories

I have processed data in excel for now, so I'll start by reading that in here to use as a starting point for this analysis.


```{r : reading in data}
Nov22_Nov23_minimal_dataset <- read.csv("C:/Users/md1rwe/Documents/Data extractions from I-CAH/Feb 2025/SDM_stats/data/Nov22-Nov23.csv", header=T, na.strings= c("", "NA"))

Nov23_Nov24_minimal_dataset <- read.csv("C:/Users/md1rwe/Documents/Data extractions from I-CAH/Feb 2025/SDM_stats/data/Nov23-Nov24.csv", header=T, na.strings= c("", "NA"))

Nov24_Feb25_minimal_dataset <- read.csv("C:/Users/md1rwe/Documents/Data extractions from I-CAH/Feb 2025/SDM_stats/data/Feb25-Nov24.csv", header=T, na.strings= c("", "NA"))
```


Let's merge Nov23-Nov24 to Nov24-Feb25
```{r : making Nov23-Feb25}
Nov23_Feb25_minimal_dataset <- rbind(Nov23_Nov24_minimal_dataset, Nov24_Feb25_minimal_dataset)

# remove the two now individual frames

remove(Nov23_Nov24_minimal_dataset, Nov24_Feb25_minimal_dataset)
```

Let's format date fields properly
```{r : formatting date fields}
Nov22_Nov23_minimal_dataset$Date.of.Assessment <- as.Date(Nov22_Nov23_minimal_dataset$Date.of.Assessment, format = "%d/%m/%Y")

Nov23_Feb25_minimal_dataset$Date.of.Assessment <- as.Date(Nov23_Feb25_minimal_dataset$Date.of.Assessment, format = "%d/%m/%Y")
```

```{r : patient stats}
# Let's look at how many patients are assessed by each centre - note that this is different from the number of patients recruited (because not every patient has necessarily been assessed). If a patient has NOT been assessed then there will be NO ENTRY into SDM registry for that patient, therefore they are, for all intents and purposes, non-existent in this analysis since there is no record of them.

patients_per_centre_Nov22_Nov23 <- Nov22_Nov23_minimal_dataset %>%
  group_by(Centre.ID.x) %>%
  summarise("number of patients assessed 22-23" = n_unique(CO.ID.x))

patients_per_centre_Nov23_Feb25 <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x) %>%
  summarise("number of patients assessed 23-25" = n_unique(CO.ID.x))  

# Now join these two data frames together so all visit info is in one frame

patients_per_centre <- full_join(patients_per_centre_Nov22_Nov23, patients_per_centre_Nov23_Feb25, by = "Centre.ID.x")
```

```{r : removing values of 0 from data frames}
# I'm doing this because values of 0 indicates data required for previous arithmetic (done in excel) is missing. For example, in the total_daily_dose_per_BSA column, if there is a 0, that means that either the total daily dose or BSA is missing.

Nov22_Nov23_minimal_dataset[Nov22_Nov23_minimal_dataset <=0] <- NA
Nov23_Feb25_minimal_dataset[Nov23_Feb25_minimal_dataset <=0] <- NA
```


```{r : 17 ohp lab values per centre, include=FALSE}
# doesn't need to be separated into females and males
OHP_22_23_sex_centre <- Nov22_Nov23_minimal_dataset %>%
  group_by(Centre.ID.x) %>%
  summarise("n" = length(X17.OHP.value[!is.na(X17.OHP.value)]),
            "mean 17OHP value" = mean(X17.OHP.value, na.rm = T),
            "median 17OHP value" = median(X17.OHP.value, na.rm = T),
            "sd 17OHP value" = sd(X17.OHP.value, na.rm = T),
            "min 17OHP value" = min(X17.OHP.value, na.rm = T),
            "max 17OHP value" = max(X17.OHP.value, na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))

OHP_23_25_sex_centre <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x) %>%
  summarise("n" = length(X17.OHP.value[!is.na(X17.OHP.value)]),
            "mean 17OHP value" = mean(X17.OHP.value, na.rm = T),
            "median 17OHP value" = median(X17.OHP.value, na.rm = T),
            "sd 17OHP value" = sd(X17.OHP.value, na.rm = T),
            "min 17OHP value" = min(X17.OHP.value, na.rm = T),
            "max 17OHP value" = max(X17.OHP.value, na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))
```

```{r : andro lab values women vs men per centre, include=FALSE}
andro_22_23_sex_centre <- Nov22_Nov23_minimal_dataset %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("n" = length(Androstenedione.value[!is.na(Androstenedione.value)]),
            "mean andro value" = mean(Androstenedione.value, na.rm = T),
            "median andro value" = median(Androstenedione.value, na.rm = T),
            "sd andro value" = sd(Androstenedione.value, na.rm = T),
            "min andro value" = min(Androstenedione.value, na.rm = T),
            "max andro value" = max(Androstenedione.value, na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))

andro_23_25_sex_centre <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("n" = length(Androstenedione.value[!is.na(Androstenedione.value)]),
            "mean andro value" = mean(Androstenedione.value, na.rm = T),
            "median andro value" = median(Androstenedione.value, na.rm = T),
            "sd andro value" = sd(Androstenedione.value, na.rm = T),
            "min andro value" = min(Androstenedione.value, na.rm = T),
            "max andro value" = max(Androstenedione.value, na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))
```

```{r : testosterone lab values women vs men per centre, include=FALSE}
testosterone_22_23_sex_centre <- Nov22_Nov23_minimal_dataset %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("n" = length(Total.testosterone.value[!is.na(Total.testosterone.value)]),
            "mean testosterone value" = mean(Total.testosterone.value, na.rm = T),
            "median testosterone value" = median(Total.testosterone.value, na.rm = T),
            "sd testosterone value" = sd(Total.testosterone.value, na.rm = T),
            "min testosterone value" = min(Total.testosterone.value, na.rm = T),
            "max testosterone value" = max(Total.testosterone.value, na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))

testosterone_23_25_sex_centre <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("n" = length(Total.testosterone.value[!is.na(Total.testosterone.value)]),
            "mean testosterone value" = mean(Total.testosterone.value, na.rm = T),
            "median testosterone value" = median(Total.testosterone.value, na.rm = T),
            "sd testosterone value" = sd(Total.testosterone.value, na.rm = T),
            "min testosterone value" = min(Total.testosterone.value, na.rm = T),
            "max testosterone value" = max(Total.testosterone.value, na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))
```

```{r : renin plasma activity women vs men per centre, include=FALSE}
renin_plas_act_22_23_sex_centre <- Nov22_Nov23_minimal_dataset %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("n" = length(Renin.plasma.activity[!is.na(Renin.plasma.activity)]),
            "mean renin value" = mean(Renin.plasma.activity, na.rm = T),
            "median renin value" = median(Renin.plasma.activity, na.rm = T),
            "sd renin value" = sd(Renin.plasma.activity, na.rm = T),
            "min renin value" = min(Renin.plasma.activity, na.rm = T),
            "max renin value" = max(Renin.plasma.activity, na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))

renin_plas_act_23_25_sex_centre <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("n" = length(Renin.plasma.activity[!is.na(Renin.plasma.activity)]),
            "mean renin value" = mean(Renin.plasma.activity, na.rm = T),
            "median renin value" = median(Renin.plasma.activity, na.rm = T),
            "sd renin value" = sd(Renin.plasma.activity, na.rm = T),
            "min renin value" = min(Renin.plasma.activity, na.rm = T),
            "max renin value" = max(Renin.plasma.activity, na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))
```

```{r : height per centre per sex, include=FALSE}
height_22_23_sex_centre <- Nov22_Nov23_minimal_dataset %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("n" = length(Height..cm.[!is.na(Height..cm.)]),
            "mean height value" = mean(Height..cm., na.rm = T),
            "median height value" = median(Height..cm., na.rm = T),
            "sd height value" = sd(Height..cm., na.rm = T),
            "min height value" = min(Height..cm., na.rm = T),
            "max height value" = max(Height..cm., na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))

height_23_25_sex_centre <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("n" = length(Height..cm.[!is.na(Height..cm.)]),
            "mean height value" = mean(Height..cm., na.rm = T),
            "median height value" = median(Height..cm., na.rm = T),
            "sd height value" = sd(Height..cm., na.rm = T),
            "min height value" = min(Height..cm., na.rm = T),
            "max height value" = max(Height..cm., na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))
```

```{r : weight per centre per sex, include=FALSE}
weight_22_23_sex_centre <- Nov22_Nov23_minimal_dataset %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("n" = length(Weight..kg.[!is.na(Weight..kg.)]),
            "mean weight value" = mean(Weight..kg., na.rm = T),
            "median weight value" = median(Weight..kg., na.rm = T),
            "sd weight value" = sd(Weight..kg., na.rm = T),
            "min weight value" = min(Weight..kg., na.rm = T),
            "max weight value" = max(Weight..kg., na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))

weight_23_25_sex_centre <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("n" = length(Weight..kg.[!is.na(Weight..kg.)]),
            "mean weight value" = mean(Weight..kg., na.rm = T),
            "median weight value" = median(Weight..kg., na.rm = T),
            "sd weight value" = sd(Weight..kg., na.rm = T),
            "min weight value" = min(Weight..kg., na.rm = T),
            "max weight value" = max(Weight..kg., na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))
```

```{r : BMI per centre per sex, include = FALSE}
BMI_22_23_data <- select(Nov22_Nov23_minimal_dataset, c("Centre.ID.x", "Sex.at.birth.x", "BMI"))
BMI_22_23_data$Category <- ""
BMI_22_23_data$Category [BMI_22_23_data$BMI <18.5] <- "Underweight"
BMI_22_23_data$Category [BMI_22_23_data$BMI >= 18.5 & BMI_22_23_data$BMI <25] <- "Normal"
BMI_22_23_data$Category [BMI_22_23_data$BMI >= 25 & BMI_22_23_data$BMI <30] <- "Overweight"
BMI_22_23_data$Category [BMI_22_23_data$BMI >=30 & BMI_22_23_data$BMI <35] <- "Obese"
BMI_22_23_data$Category [BMI_22_23_data$BMI >=35] <- "Extremely obese"
BMI_22_23_data$Category [BMI_22_23_data$Category == ""] <- "Missing"

BMI_22_23_sex_centre <- BMI_22_23_data %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("n" = length(BMI[!is.na(BMI)]),
            "mean BMI value" = mean(BMI, na.rm = T),
            "median BMI value" = median(BMI, na.rm = T),
            "sd BMI value" = sd(BMI, na.rm = T),
            "min BMI value" = min(BMI, na.rm = T),
            "max BMI value" = max(BMI, na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))

BMI_categories_22_23_sex_centre <- BMI_22_23_data %>%
  group_by(Centre.ID.x, Sex.at.birth.x, Category) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = "Category",
              values_from = "n")


#
BMI_23_25_data <- select(Nov23_Feb25_minimal_dataset, c("Centre.ID.x", "Sex.at.birth.x", "BMI"))
BMI_23_25_data$Category <- ""
BMI_23_25_data$Category [BMI_23_25_data$BMI <18.5] <- "Underweight"
BMI_23_25_data$Category [BMI_23_25_data$BMI >= 18.5 & BMI_23_25_data$BMI <25] <- "Normal"
BMI_23_25_data$Category [BMI_23_25_data$BMI >= 25 & BMI_23_25_data$BMI <30] <- "Overweight"
BMI_23_25_data$Category [BMI_23_25_data$BMI >=30 & BMI_23_25_data$BMI <35] <- "Obese"
BMI_23_25_data$Category [BMI_23_25_data$BMI >=35] <- "Extremely obese"
BMI_23_25_data$Category [BMI_23_25_data$Category == ""] <- "Missing"

BMI_23_25_sex_centre <- BMI_23_25_data %>%
  group_by(Centre.ID.x, Sex.at.birth.x) %>%
  summarise("n" = length(BMI[!is.na(BMI)]),
            "mean BMI value" = mean(BMI, na.rm = T),
            "median BMI value" = median(BMI, na.rm = T),
            "sd BMI value" = sd(BMI, na.rm = T),
            "min BMI value" = min(BMI, na.rm = T),
            "max BMI value" = max(BMI, na.rm = T)) %>%
  mutate_if(is.numeric, ~round(.,2))

BMI_categories_23_25_sex_centre <- BMI_23_25_data %>%
  group_by(Centre.ID.x, Sex.at.birth.x, Category) %>%
  summarise(n = n()) %>%
  pivot_wider(names_from = "Category",
              values_from = "n")

```




Medication stats
```{r : individual dose stats, per medication, per centre, include=FALSE}
dose_stats_22_23 <- Nov22_Nov23_minimal_dataset %>%
  group_by(Centre.ID.x, Medicine_1.x) %>%
  summarise("n Medicine_1.x" = length(Medicine_1.x[!is.na(Medicine_1.x)]),
            "mean Medicine_1.x value" = mean(Standardised.doses_1, na.rm = T),
            "median Medicine_1.x value" = median(Standardised.doses_1, na.rm = T),
            "sd Medicine_1.x value" = sd(Standardised.doses_1, na.rm = T),
            "min Medicine_1.x value" = min(Standardised.doses_1, na.rm = T),
            "max Medicine_1.x value" = max(Standardised.doses_1, na.rm = T),
            
            "n Medicine_2.x" = length(Medicine_2.x[!is.na(Medicine_2.x)]),
            "mean Medicine_2.x value" = mean(Standardised.doses_2, na.rm = T),
            "median Medicine_2.x value" = median(Standardised.doses_2, na.rm = T),
            "sd Medicine_2.x value" = sd(Standardised.doses_2, na.rm = T),
            "min Medicine_2.x value" = min(Standardised.doses_2, na.rm = T),
            "max Medicine_2.x value" = max(Standardised.doses_2, na.rm = T),
            
            "n Medicine_3.x" = length(Medicine_3.x[!is.na(Medicine_3.x)]),
            "mean Medicine_3.x value" = mean(Standardised.doses_3, na.rm = T),
            "median Medicine_3.x value" = median(Standardised.doses_3, na.rm = T),
            "sd Medicine_3.x value" = sd(Standardised.doses_3, na.rm = T),
            "min Medicine_3.x value" = min(Standardised.doses_3, na.rm = T),
            "max Medicine_3.x value" = max(Standardised.doses_3, na.rm = T),
            
            "n Medicine_4.x" = length(Medicine_4.x[!is.na(Medicine_4.x)]),
            "mean Medicine_4.x value" = mean(Standardised.doses_4, na.rm = T),
            "median Medicine_4.x value" = median(Standardised.doses_4, na.rm = T),
            "sd Medicine_4.x value" = sd(Standardised.doses_4, na.rm = T),
            "min Medicine_4.x value" = min(Standardised.doses_4, na.rm = T),
            "max Medicine_4.x value" = max(Standardised.doses_4, na.rm = T),
            
            ) %>%
  mutate_if(is.numeric, ~round(.,2))

# remove Inf, -Inf and NaN values
dose_stats_22_23[dose_stats_22_23 == "Inf"] <- NA
dose_stats_22_23[dose_stats_22_23 == "-Inf"] <- NA
dose_stats_22_23[dose_stats_22_23 == "NaN"] <- NA

# Now for other time frame
dose_stats_23_25 <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x, Medicine_1.x) %>%
  summarise("n Medicine_1.x" = length(Medicine_1.x[!is.na(Medicine_1.x)]),
            "mean Medicine_1.x value" = mean(Standardised.doses_1, na.rm = T),
            "median Medicine_1.x value" = median(Standardised.doses_1, na.rm = T),
            "sd Medicine_1.x value" = sd(Standardised.doses_1, na.rm = T),
            "min Medicine_1.x value" = min(Standardised.doses_1, na.rm = T),
            "max Medicine_1.x value" = max(Standardised.doses_1, na.rm = T),
            
            "n Medicine_2.x" = length(Medicine_2.x[!is.na(Medicine_2.x)]),
            "mean Medicine_2.x value" = mean(Standardised.doses_2, na.rm = T),
            "median Medicine_2.x value" = median(Standardised.doses_2, na.rm = T),
            "sd Medicine_2.x value" = sd(Standardised.doses_2, na.rm = T),
            "min Medicine_2.x value" = min(Standardised.doses_2, na.rm = T),
            "max Medicine_2.x value" = max(Standardised.doses_2, na.rm = T),
            
            "n Medicine_3.x" = length(Medicine_3.x[!is.na(Medicine_3.x)]),
            "mean Medicine_3.x value" = mean(Standardised.doses_3, na.rm = T),
            "median Medicine_3.x value" = median(Standardised.doses_3, na.rm = T),
            "sd Medicine_3.x value" = sd(Standardised.doses_3, na.rm = T),
            "min Medicine_3.x value" = min(Standardised.doses_3, na.rm = T),
            "max Medicine_3.x value" = max(Standardised.doses_3, na.rm = T),
            
            "n Medicine_4.x" = length(Medicine_4.x[!is.na(Medicine_4.x)]),
            "mean Medicine_4.x value" = mean(Standardised.doses_4, na.rm = T),
            "median Medicine_4.x value" = median(Standardised.doses_4, na.rm = T),
            "sd Medicine_4.x value" = sd(Standardised.doses_4, na.rm = T),
            "min Medicine_4.x value" = min(Standardised.doses_4, na.rm = T),
            "max Medicine_4.x value" = max(Standardised.doses_4, na.rm = T),
            
            ) %>%
  mutate_if(is.numeric, ~round(.,2))

# remove Inf, -Inf and NaN values
dose_stats_23_25[dose_stats_23_25 == "Inf"] <- NA
dose_stats_23_25[dose_stats_23_25 == "-Inf"] <- NA
dose_stats_23_25[dose_stats_23_25 == "NaN"] <- NA

```

```{r : total daily dose trends per medication, per centre, include=FALSE}
# will need to factor in whether patients are on single or combined therapies...
# or do I? If doses are standardised then is this relevant?

# let's make a new frame to determine which patients are on single or combined therapies:
therapy_22_23 <- select(Nov22_Nov23_minimal_dataset, c("Centre.ID.x", "CO.ID.x", "Medicine_1.x", "Medicine_2.x", "Medicine_3.x", "Medicine_4.x"))
therapy_23_25 <- select(Nov23_Feb25_minimal_dataset, c("Centre.ID.x", "CO.ID.x", "Medicine_1.x", "Medicine_2.x", "Medicine_3.x", "Medicine_4.x"))

# remove rows with NO MEDICATION DATA
therapy_22_23 <- therapy_22_23 [!is.na(therapy_22_23$Medicine_1.x),]
therapy_23_25 <- therapy_23_25 [!is.na(therapy_23_25$Medicine_1.x),]

therapy_22_23$"single/combined" <- NA
therapy_23_25$"single/combined" <- NA

# check for single
therapy_22_23$`single/combined` <-
  ifelse(!is.na(therapy_22_23$Medicine_1.x) &
         (is.na(therapy_22_23$Medicine_2.x) & is.na(therapy_22_23$Medicine_3.x) & is.na(therapy_22_23$Medicine_4.x) |
          therapy_22_23$Medicine_1.x == therapy_22_23$Medicine_2.x & is.na(therapy_22_23$Medicine_3.x) & is.na(therapy_22_23$Medicine_4.x) |
          therapy_22_23$Medicine_1.x == therapy_22_23$Medicine_2.x & therapy_22_23$Medicine_1.x == therapy_22_23$Medicine_3.x & is.na(therapy_22_23$Medicine_4.x) |
          therapy_22_23$Medicine_1.x == therapy_22_23$Medicine_2.x & therapy_22_23$Medicine_1.x == therapy_22_23$Medicine_3.x & therapy_22_23$Medicine_1.x == therapy_22_23$Medicine_4.x),
          as.character("single"),
          as.character("combined"))

therapy_23_25$`single/combined` <-
  ifelse(!is.na(therapy_23_25$Medicine_1.x) &
         (is.na(therapy_23_25$Medicine_2.x) & is.na(therapy_23_25$Medicine_3.x) & is.na(therapy_23_25$Medicine_4.x) |
          therapy_23_25$Medicine_1.x == therapy_23_25$Medicine_2.x & is.na(therapy_23_25$Medicine_3.x) & is.na(therapy_23_25$Medicine_4.x) |
          therapy_23_25$Medicine_1.x == therapy_23_25$Medicine_2.x & therapy_23_25$Medicine_1.x == therapy_23_25$Medicine_3.x & is.na(therapy_23_25$Medicine_4.x) |
          therapy_23_25$Medicine_1.x == therapy_23_25$Medicine_2.x & therapy_23_25$Medicine_1.x == therapy_23_25$Medicine_3.x & therapy_23_25$Medicine_1.x == therapy_23_25$Medicine_4.x),
          as.character("single"),
          as.character("combined"))

```

```{r : total daily dose per  centre}
total_doses_22_23 <- Nov22_Nov23_minimal_dataset %>%
  group_by(Centre.ID.x) %>%
  summarise(mean_total_dose = mean(total_standardised_daily_dose_1_1, na.rm = T),) %>%
  mutate_if(is.numeric, ~round(.,2))

total_doses_23_25 <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x) %>%
  summarise(mean_total_dose = mean(total_standardised_daily_dose_1_1, na.rm = T),
            n = n()) %>%
  mutate_if(is.numeric, ~round(.,2))



```

```{r : how many patients on each medication for each dose, per centre}
first_dose_medicine <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x, Medicine_1.x) %>%
  summarise("first dose" = n())

second_dose_medicine <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x, Medicine_2.x) %>%
  summarise("second dose" = n())

third_dose_medicine <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x, Medicine_3.x) %>%
  summarise("third dose" = n())

fourth_dose_medicine <- Nov23_Feb25_minimal_dataset %>%
  group_by(Centre.ID.x, Medicine_4.x) %>%
  summarise("fourth dose" = n())

test <- cbind(first_dose_medicine, second_dose_medicine$`second dose`)

### want to add in third and fourth dose counts to test frame

```


```{r : end of script section}
print("Script complete")
```





